Playing multiple games using deep reinforcement learning, or Spatial Attention network can play (beat) simultaneously multiple games in reinforcement learning

### 2019-09-15 multi_dqn_paper/paper.tex
updated results

\subsection {Network architecture}
Following state of the art \cite{bib:vgg_net} and \cite{bib:resnet_net}, we used only 3x3 kernels with stride 1, instead of \cite{bib:dqn_atari} 8x8 kernels.
As activation function the ELU is choosen, with $\alpha = 0.1$. After convolution and pooling layer we used one full connected with 256 units and second
full connected corresponding to actions count in game. For multi\_nets the amount of units on last layer depends on game with maximum possible actions.

>>>>

\subsection {Network architecture}
Following state of the art \cite{bib:vgg_net} and \cite{bib:resnet_net}, we used only 3x3 kernels with stride 1, instead of 8x8 kernels as in \cite{bib:dqn_atari}.
As activation function the ELU is choosen, with $\alpha = 0.1$. After convolution and pooling layer we used one full connected with 256 units and second
full connected corresponding to actions count in game. For multi\_nets the amount of units on last layer depends on game with maximum possible actions.
